### 2022-01-27 input/experiments.tex
small fix in intro, url in expe, replaced enriched in proposal

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations we conducted on top of
PeerSim, a simulator that allows researchers to
evaluate and assess distributed algorithms in large scale
networks~\cite{montresor2009peersim}. All the code is available on the
Github platform at \url{https://anonymous.4open.science/r/peersim-partition-5592} \note{fix URL}.

@@

\subsection{Scalability}
\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

\subsection{Trafic containment}
\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in the context of dynamic
  inter-autonomous system communications.

@@

\subsection{Cross \NAME}
\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper.} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.

>>>>

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations conducted on PeerSim, a
simulator that allows researchers to evaluate and assess distributed
algorithms in large scale networks~\cite{montresor2009peersim}. All
the code is available on the Github platform at
\mbox{\url{https://github.com/ane-wane/as-cast}}.

@@

\subsection{Scalability and trade-off}
\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

\subsection{Traffic containment}
\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in the context of dynamic
  inter-autonomous system communications.

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper.} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.

### 2022-01-27 input/proposal.tex
small fix in intro, url in expe, replaced enriched in proposal

\begin{definition}[\label{def:forwarding}Forwarding]
  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
  \underline{s}ends $s_{xy}(m)$ the latter to all its neighbors $y$
  \TODO{enriched} ($\oplus$) with metadata that depends on its local
  knowledge $\sigma_x$:
  $f_x(m) \implies \forall \langle x, y\rangle \in E: s_{xy}(m
  \TODO{\oplus} \sigma_x)$.
\end{definition}

>>>>

\begin{definition}[\label{def:forwarding}Forwarding]
  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
  \underline{s}ends the latter ($s_{xy}(m)$) to all its neighbors $y$
  accumulating or aggregating ($\oplus$) metadata that depends on its
  local knowledge $\sigma_x$: $f_x(m) \implies \forall \langle x,
  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
\end{definition}
